\input{texdefs}

\begin{document}

\frontmatter

\title{
    {\bf Scaling Wearable Cognitive Assistance}
}
\author{Junjue Wang}
\date{May 2020}
\Year{2020}
\trnumber{CMU-CS-20-107}

\vspace{3cm}

\committee{
    Mahadev Satyanarayanan (Satya) (Chair), Carnegie Mellon University\\
    Daniel Siewiorek, Carnegie Mellon University \\
    Martial Hebert, Carnegie Mellon University \\
    Roberta Klatzky, Carnegie Mellon University \\
    Padmanabhan Pillai, Intel Labs
}

\support{This research was supported by the National Science Foundation (NSF)
    under grant number CNS-1518865. Additional support was provided by Intel,
    Vodafone, Deutsche Telekom, Verizon, Crown Castle, Seagate, VMware,
    MobiledgeX, InterDigital, and the Conklin Kistler family fund.}
% \disclaimer{}

% copyright notice generated automatically from Year and author.
% permission added if \permission{} given.

\keywords{Wearable Cognitive Assistance, Scalability, Adaptation, Wearable Computing, Augmented Reality, Edge Computing, Cloudlet}

\maketitle

\begin{dedication}
    To the future of machines.
\end{dedication}

%% Obviously, it's probably a good idea to break the various sections of your thesis
%% into different files and input them into this file...

\begin{abstract}
    It has been a long endeavour to augment human cognition with machine
    intelligence. Recently, a new genre of applications, named Wearable
    Cognitive Assistance, has advanced the boundaries of augmented cognition.
    These applications continuously process data from body-worn sensors and
    provide just-in-time guidance to help a user complete a specific task. While
    previous research has demonstrated the technical feasibility of wearable
    cognitive assistants, this dissertation addresses the problem of
    \textit{scalability}. We identify two critical challenges to the widespread
    deployment of these applications to be 1) the need to operate cloudlets and
    wireless network at low utilization to achieve acceptable end-to-end latency
    2) the level of specialized skills and the long development time needed to
    create new applications. To address these challenges, we first design and
    evaluate adaptation-centric optimizations that reduce resource consumption
    and improve resource management in contentious systems while maintaining
    acceptable end-to-end latency. We then propose and implement a new
    prototyping methodology and a suite of development tools to lower the
    barrier of application development.
\end{abstract}

\begin{acknowledgments}
    I have been extremely fortunate to be inspired and supported by a group of
    talented and caring individuals throughout my PhD research. This
    dissertation would not be possible without them.

    I am deeply indebted to my advisor Mahadev Satyanarayanan (Satya), who
    played a paramount role in guiding me through this dissertation research. Satya
    taught me how to design, implement, and evaluate mobile and distributed systems.
    His knowledge and encouragement have been a constant source of inspiration for
    me to work harder and produce more impactful system research. In addition to an
    excellent academic advisor, Satya has also been a visionary mentor whom I look
    up to. It has been invaluable for me to observe and learn from his leadership in
    shaping new technologies and bringing people together for a shared vision.
    Another person who has inspired and helped me tremendously is Padmanabhan (Babu)
    Pillai. He is an exemplary researcher with broad and deep knowledge, kindness,
    and patience. In addition, I would like to thank my thesis committee members,
    Daniel Siewiorek, Martial Hebert, and Roberta (Bobby) Klatzky. As this
    dissertation is at the intersection of multiple fields, they have given me many
    insightful feedback and guidance on human-computer interaction and computer
    vision. Their comments from our weekly meetings have been vital for me to stay
    on the correct course.

    Brilliant and kind individuals in Satya's research group have
    provided many rapport and joy during my PhD study. In addition, many ideas
    and experimental results presented in this dissertation come from close
    collaborative work with them. They have also provided many system
    infrastructure support to perform the experiments. I cannot dream of a
    better team and environment to be in for a PhD student. My day-to-day
    interactions with them helped me grow as a better researcher and a critical
    thinker. Especially, I would like to give my appreciation to, in an
    alphabetical order, Yoshihisa Abe, Brandon Amos, Jim Blakley, Zhuo Chen, Tom
    Eiszler, Ziqiang (Edmond) Feng, Shilpa George, Kiryong Ha, Jan Harkes, Wenlu
    Hu, Roger Iyengar, Natalie Janosik, and Haithem Turki. I also want to thank
    Chase Klingensmith for his outstanding administrative assistance for the
    group.

    My PhD research has also benefited significantly from the larger research
    community. I was fortunate enough to collaborate with many exceptional
    academic researchers and industry professionals in the past few years. Thank
    you all for the inspiration you have given me. In particular, thank you,
    Pauline Anthonysamy, Mihir Bala, Richard Buchler, Kevin Christensen, Anupam
    Das, Nigel Davies, Debidatta Dwibedi, Khalid Elgazzar, Wei Gao, Ying Gao,
    James Gross, Alex Guerrero, Guenter Klas, Zico Kolter, Michael Kozuch,
    Hongkun Leng, Grace Lewis, Tan Li, Haodong Liu, Yuqi Liu, Lin Ma, Mateusz
    Mikusz, Manuel Olguín, Sai Teja Peddinti, Truong An Pham, Norman Sadeh, Rolf
    Schuster, Asim Smailagic, Nihar B. Shah, Nina Taft, Joseph Wang, Guanhang
    Wu, Yu Xiao, Shao-Wen Yang, Canbo (Albert) Ye, and Siyan Zhao.

    My beloved family and friends have provided enormous understanding,
    sympathy, and support throughout my PhD study. I could not have finished
    this thesis research without knowing they are on my back. In particular, I
    have always felt extremely lucky and gracious to be born to the most
    attentive, considerate, and wise parents in the world. They instilled the
    value of perseverance and compassion early in my life through examples.
    Without their trust and encouragement, I would never dream of completing a
    doctorate degree halfway around the globe at one of the finest computer
    science institutions in the world. Furthermore, as lucky as a man could be,
    I met my dearest partner, Han, while pursuing my PhD. Since then, she has
    been my closest friend and most cherished counselor who has provided an
    immeasurable amount of love, strength, and comfort. I am able to become a
    better version of myself because of her. As much as this dissertation is
    written for the future of machines, it is the unwritten words about people
    that will be treasured for the rest of my life.

\end{acknowledgments}

\tableofcontents
\listoffigures
\listoftables
\mainmatter

%% Double space document for easy review:
%\renewcommand{\baselinestretch}{1.66}\normalsize

% The other requirements Catherine has:
%
%  - avoid large margins.  She wants the thesis to use fewer pages, 
%    especially if it requires colour printing.
%
%  - The thesis should be formatted for double-sided printing.  This
%    means that all chapters, acknowledgements, table of contents, etc.
%    should start on odd numbered (right facing) pages.
%
%  - You need to use the department standard tech report title page.  I
%    have tried to ensure that the title page here conforms to this
%    standard.
%
%  - Use a nice serif font, such as Times Roman.  Sans serif looks bad.
%
% Other than that, just make it look good...

\input{intro}
\input{background}
\input{bandwidth-reduction}
\input{workload-reduction}
\input{cloudlet-resource-management}
\input{app-dev}
% \input{app-deploy}
\input{conclusion}

\backmatter

%\renewcommand{\baselinestretch}{1.0}\normalsize

% By default \bibsection is \chapter*, but we really want this to show
% up in the table of contents and pdf bookmarks.
\renewcommand{\bibsection}{\chapter{\bibname}}
%\newcommand{\bibpreamble}{This text goes between the ``Bibliography''
%  header and the actual list of references}
\bibliographystyle{plainnat}
\bibliography{thesis} %your bib file

\end{document}
